% % Glossary entries
%
\newglossaryentry{bluetooth}
{
	name=Bluetooth,
	plural=Bluetooth,
	description={Bluetooth is a wireless technology standard for exchanging data over short distances. (Wikipedia)},
}
\newglossaryentry{ble}
{
	name=Bluetooth Low Energy,
	plural=Bluetooth Low Energy,
	description={Bluetooth Low Energy (Bluetooth LE, colloquially BLE, formerly marketed as Bluetooth Smart) is a wireless personal area network technology aimed at novel applications in the healthcare, fitness, beacons, security, and home entertainment industries. (Wikipedia)}
}
\newacronym{MAC}{MAC Address}{A media access control address (MAC address) of a device is a unique identifier assigned to a network interface controller for communications at the data link layer of a network segment. (Wikipedia)}

\newacronym{GPX}{GPX}{GPS Exchange Format is an open format that can be used to describe geolocation data.}

\newacronym{TLS}{TLS}{Transport Secure Layer is a communications protocol designed to provide security.}

\newglossaryentry{server}
{
	name=Server,
	plural=Servers,
	description={Central server the \gls{app} communicates with.},
}
\newglossaryentry{beacon}
{
	name=BT-Device,
	plural=BT-Devices,
	description={A \gls{bluetooth} or \gls{ble} device broadcasting a unique, constant \acrshort{MAC} and support pairing.},
}
\newglossaryentry{backoffice}
{
	name=Backoffice,
	plural=Backoffices,
	description={The administrative web-interface of the \gls{server}.},
}
\newglossaryentry{app}
{
	name=App,
	plural=Apps,
	description={The Android application described in this document.},
}
\newglossaryentry{backoffice account}
{
	name=Backoffice Account,
	plural=Backoffice Accounts,
	description={An account that can be used to log in to the \gls{backoffice}.},
}
\newglossaryentry{user account}
{
	name=User Account,
	plural=User Accounts,
	description={An account that can be used to log in to the \gls{app}.},
}
\newglossaryentry{backend}
{
	name=Backend,
	plural=Backends,
	description={The RESTful API of the \gls{server}.},
}
\newglossaryentry{user}
{
	name=User,
	plural=Users,
	description={Regular users that (might) use the \gls{app}.},
}
\newglossaryentry{administrator}
{
	name=Administrator,
	plural=Administrators,
	description={An administrative user that manages the \gls{server} through the \gls{backoffice}.},
}
\newglossaryentry{public api}
{
	name=Public API,
	plural=Public APIs,
	description={The public variant of our RESTful API that can be used by external services to access functionality on our \gls{server}.},
}
\newglossaryentry{IoT}
{
	name=IoT,
	description={Internet of Things - is a network of physical and virtual devices that exchange data to improve their capabilities.}
}
\newglossaryentry{GPS}
{
	name=GPS,
	description={Global Positioning System - is a satellite based navigation system. It provides a very accurate geolocation signal anywhere on earth with a direct line of sight to at least four GPS-satellites.}
}
\newglossaryentry{SIM card}
{
	name=SIM Card,
	description={A subscriber identity module is a small circuit that allows mobile communication providers to identify and authenticate service users. It is usually necessary to establish a data connection over the mobile communication network.}
}
\newglossaryentry{PayPal}
{
	name=PayPal,
	description={Paypal is an online payment provider. It is used to transfer small amounts of money between parties in online commerce. }
}
\newglossaryentry{osm}
{
	name=OSM,
	description={Open Street Map is an open source collaborative provider of geodata and world maps.}
}
\newglossaryentry{gmaps}
{
	name=Google Maps,
	description={Google Maps is a commercial provider of geodata and world maps.}
}
\newglossaryentry{bloomfilter}
{
	name=Bloom filter,
	description={A Bloom filter is a space-efficient probabilistic data structure that is used to test whether an element is a member of a set. False positive matches are possible, but false negatives are not. (Wikipedia)}
}

\glsaddall
\makenoidxglossaries