\chapter{Test Cases Testing}

\section{Mandatory features}
\begin{itemize}
	\item{GTC-1} Covered by GTC-2.
	\item{GTC-2} Automated test passed.
	\item{GTC-3} Automated test passed.
	\item{GTC-4} Automated test passed.
	\item{GTC-5} Not applicable.
	\item{GTC-6} Automated test passed.
	\item{GTC-7} Automated test passed.
	\item{GTC-8} Automated test passed.
	\item{GTC-9} Automated test passed.
	\item{GTC-10-1} Automated test partially passed \\ Login activity is displayed after successful sign up instead of the Dashboard activity
	\item{GTC-10-2} Automated test partially passed \\ Duplicate account is correctly not created, but no error is displayed and the user is sent back to the Login activity
	\item{GTC-11-1} Automated test passed.
	\item{GTC-11-2} Automated test passed.
	\item{GTC-12-1} Automated test passed.
	\item{GTC-12-2} Passed. \\ (Indirectly tested due to the way, automated tests are implemented)
	\item{GTC-13} Automated test passed.
	\item{GTC-14} Automated test passed.
	\item{GTC-15-1} Automated test passed.
	\item{GTC-15-2} Automated test passed.
	\item{GTC-16} Automated test passed.
	\item{GTC-17} Manual test passed. \\ Cannot be automated since it depends on a specific device being carried away by a second person.
	\item{GTC-18} Automated test passed.
	\item{GTC-19} Automated test passed.
	\item{GTC-20} Automated test passed.
	\item{GTC-21} Manual test passed. \\ User data was correctly synchronized between multiple devices.
\end{itemize}

\section{Optional features}
\begin{itemize}
	\item{GTCO-3} Manual test passed.
	\item{GTCO-4} Manual test passed.
	\item{GTCO-5-1} Manual test passed.
	\item{GTCO-5-2} Manual test passed.
	\item{GTCO-6} Manual test passed.
	\item{GTCO-7} Manual test passed.
	\item{GTCO-8} Manual test failed. \\ Password was changed successfully, but neither session was invalidated. \\ Additionally the password change resulted in total data loss as user data was still encrypted using the old password.
\end{itemize}